Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor edit to IDE neural field model

The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)

>>>>

The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
